\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{amsmath}

% moderncv themes
\moderncvstyle{banking}
\moderncvcolor{blue}  

\usepackage[utf8]{inputenc}
\usepackage[scale=0.785]{geometry}

\definecolor{blue}{rgb}{0.22, 0.45, 0.698}
\newcommand\Colorhref[3][blue]{\href{#2}{\small\color{#1}#3}}

\usepackage{import}

% personal data
\name{Yi}{Zhen}
\title{Curriculum Vitae}
\address{11-502, Pusan Rd, Pudongxin District}{Shanghai 200000}{China}
\mobile{+86~177~1768~7328}
\email{iamzhenyi@gmail.com}
\homepage{izhen.me}
\social[github]{i-zhen} 
\social[linkedin]{izhenyi} 
%\quote{Keep It Simple and Stupid} 

\begin{document}
\makecvtitle

\section{Experience}
\begin{itemize}
	\item Apr. 2017 -- Present, Software Engineer, \Colorhref[blue]{http://www.citigroup.com/china/csts/}{\textit{Citigroup Inc.}}, Shanghai, P.R.China
	\item Feb. 2014 -- Apr. 2014, Research Assistant Intern, \Colorhref[blue]{http://www.compsci.sysu.edu.cn/cn/cn01/index.htm}{\textit{Guangdong Province Key Laboratory of Computational Science}}, Guangzhou, P.R.China
\end{itemize}

\section{Miscellaneous}
\subsection{Job Projects}
%\item{
\cventry{Aug. 2017 -- Present}{Wire Transfer system for block trading agent}{\textsf{WIRE}}{engineer at Citigroup}{}{
	Customers book payment, pre-advice and deposit wire transfers on the platform
	\begin{itemize}
		\item Full-stack development for Currency Eligibility module: Developed front-end using MVC model with the help of Ext JS. Implemented CRUD, approval and drill-down analysis of Available Straddle value. Using Facade, Factory and Dynamic Proxy patterns designed and implemented controller, services and DAO for back-end
		\item Developed reconciliation module for downstream data warehouse team: abstracted business logic to TCP-like 3-way handshake protocol through FSM.
Implemented asynchronous unmarshalling message ability
		\item Debugging existing bugs and analyzing daily logs. Continuous Integration
	\end{itemize}
}
%}
%\item{
\cventry{Apr. 2017 -- Aug. 2017}{Anti money laundering platform}{\textsf{EWARA}}{engineer at Citigroup}{}{
	\begin{itemize}
		\item Implemented approval logic for tree-form entities. Developed general DAO for arbitrary tables by JDBC
		\item Participated in email alert ability implementation, RESTful API design, PDF report module enhancement
		\item Using reflection techniques to extend POJO test module for automation unit test
	\end{itemize}
}
%}
%\item{
\cventry{Jun. 2017 -- Aug. 2017}{Experimental AI project}{\textsf{HAMSTER}}{engineer at Citigroup}{}{
   	Recognition and NLP for scanning image of bank statement. Writing and debugging image alignment algorithm
}
%}

\subsection{Side Projects}
%\begin{itemize}
%\item{
\cventry{Nov. 2016 -- Jan. 2017}{web app}{\textsf{Project Lambda}}{founder}{}{
   	A Hacker-News-like social information platform focusing on IT industry and computer science, which users could publish general news, academic contents and questions through it. Reducing time wasting on nonnutritive information is the major goal
	\begin{description}
		\item[Keywords] Haskell 8.0.2, Scotty, Persistent, mime-mail, websockets, Blaze, PostgreSQL, Bootstrap, jQuery
		\item[Github Address] \texttt{https://github.com/ProLambda/Times}
		\item[Chinese Blog Article] \texttt{https://izhen.me/2017/08/20/aws-lambda/}
		%\item[Hello] ~
		%	\begin{itemize}
		%		\item Machine learning and its applications in natural language processing
		%	\end{itemize}
	\end{description}
}
%}

%\item{
\cventry{Jun. 2016 -- Aug. 2016}{Haskell Library - 1413 times download till 05/27/2018}{\textsf{PPrinter: A generic derivable Haskell pretty printer}}{author}{}{
   	PPrinter is a Haskell library that supports automatic derivation of pretty printing functions on user defined arbitrary data types (the deriving mechanism supports the automatic generation of instances for functions)
	\begin{description}
		\item[Keywords] Dissertation Project, Hackage, Haskell 7.10.2
		\item[Hackage Address] \texttt{http://hackage.haskell.org/package/PPrinter-0.1.0}
	\end{description}
}
%}

%\item{
\cventry{Oct. 2015 -- Dec. 2015}{system software}{\textsf{Compiler of Small-C}}{developer}{}{
   	A compiler for the subset of C language that compiles the source code to Java bytecode. It contains the essential parts of a standard compiler including lexer, parser, semantic analyzer and code generator
		\begin{description}
		\item[Keywords] Java 7, ASM 4
		\item[Github Address] \texttt{https://github.com/i-zhen/Reactor-C}
	\end{description}
}
%}

%\item{
\cventry{Oct. 2015 -- Oct. 2015}{local app}{\textsf{Interpreter of ML-like Programming Language}}{developer}{}{
   	An interpreter written in scala for a simple ML-like programming language which supports syntactic sugar, type checking, recursive function and first-order lambda calculus
	\begin{description}
		\item[Keywords] Scala 2.11.7
		\item[Github Address] \texttt{https://github.com/i-zhen/Apache-Longbow}
	\end{description}
}
%}

%\item{
\cventry{Apr. 2013 -- Jun. 2013}{web app}{\textsf{The Student Activity Center(SAC) Room Reservation System}}{full-stack developer}{not open source}{
   	Designed a room reservation system for the Student Activity Center in Sun Yat-sen University. Students can use this system to book rooms in SAC and managed their own information
	\begin{description}
		\item[Keywords] Python 2.7.5, Javascript, MySQL, web.py, Bootstrap, jQuery
	\end{description}
}
%}

\subsection{School Team}
\cventry{2014}{Team member}{Sun Yat-sen University ASC Student Supercomputer Challenge Team}{}{}{
    \begin{itemize}
    	\item ASC14 required the team to wring the most HPC performance out of a 3000W power allowance
        	\item Mastered the numerical methods,  relevant algorithms, heterogeneous and multiprocessor programming
	\item Optimized the SU$^{2}$ -- a Stanford University developed open-source C++ code for PDE analysis and designed things that adhere to PDE constraints, and assisted in the HPL event
	\end{itemize}
}

%\end{itemize}

\section{Professional Skills}
\subsection{Programming Language and Framework}
\cvitem{Language}{Haskell, Java, C/C++, Python, Ruby, Swift, Ocaml, Scala, Prolog, Coq, Isabelle}
\cvitem{Framework}{Spring, JMS, Ext JS, JUnit, Mockito, JDBC, Logger, Java servlet, SQL, Jaxb2Marshaller}
\cvitem{Tools}{Jenkins, uDeploy, AutoSys, JIRA, Git, SonarQube, Amazon EC2, NuSMV, Vim, Eclipse, \LaTeX}

\section{Awards}
\cventry{2014}{The ASC Student Supercomputer Challenge (ASC14)}{First Prize and Highest Linpack Award}{}{}{Set a new world record of HPL(Linpack) performance and won ¥10,000 CNY}
\cventry{2014}{The ACM-ICPC China Guangdong Provincial Programming Contest (GDCPC)}{Bronze Medal (Third Prize)}{}{}{}
\cventry{2009\&2008}{The National Olympiad in Informatics in Provinces (NOIP)}{Two-time recipient of First Prize}{}{}{}

\section{Education}
\cventry{Sep. 2015 -- Nov. 2016}
{Master of Science in Artificial Intelligence}
{University of Edinburgh}
{Edinburgh, U.K.}
{\textit{Pass with Merit}}
{Dissertation: Deriving Pretty-printing for Haskell, supervised by Prof. Philip Wadler}

\cventry{Sep. 2011 -- Jun. 2015}
{Bachelor of Engineering in Software Engineering}
{Sun Yat-sen University}
{Guangzhou, P.R.China}
{GPA \textit{: 3.3}}
{Recommended for admission to SYSU and exempted from Gaokao because of well performance at NOIP}

\end{document}
